Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
some minor changes by yny

The dynamics of weakly adhesive vesicles under various flowing conditions is investigated numerically using a boundary integral formulation with
adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, two nearby vesicles 
move slowly towards each other under the adhesive potential, pushing out fluid in the gap to  
form a doublet at equilibrium. A lubrication analysis on such draining of the
thin film gives the dependencies of draining time on adhesion strength and separation distance that are in good agreement with results from
boundary integral simulations.
%
In a microfluid trap where the stagnation of an extensional flow  is placed in the middle of a vesicle doublet through an active control loop,
novel dynamics of a vesicle double tis observed. Results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a doublet the effective shear viscosity of a dilute suspension of vesicle doublets is found 
to be a function of both reduced area and the adhesion strength.
Results from these numerical studies and analysis shed light on the hydrodynamic effects of adhesive interactions between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

>>>>

The dynamics of weakly adhesive vesicles under various flowing conditions is investigated numerically using a boundary integral formulation with
adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, two nearby vesicles 
move slowly towards each other under the adhesive potential, pushing out fluid in the gap to  
form a doublet at equilibrium. A lubrication analysis on such draining of the
thin film gives the dependencies of draining time on adhesion strength and separation distance that are in good agreement with results from
boundary integral simulations.
%
In a microfluid trap where the stagnation of an extensional flow  is placed in the middle of a vesicle doublet through an active control loop,
novel dynamics of a vesicle doublet is observed. Results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a doublet the effective shear viscosity of a dilute suspension of vesicle doublets is found 
to be a function of both reduced area and the adhesion strength.
Results from these numerical studies and analysis shed light on the hydrodynamic effects of adhesive interactions between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}
